### 2015-07-15 rscripts/data_review.Rmd
incipient user cluster pictures

## handle day splits:
## if login_day == logout_day
##  (floor(login_time/3600) <= hour) & (hour  <= floor(logout_time/3600))
## else - n.b., already precluded logout_time > login_time, since enforced < 24hr sessions
##  hour >= login | hour <= logout

comp.user.short <- setkey(rbindlist(
  Map(function(hour) censor.dt[
    ((login_day == logout_day) & (floor(login_time/3600) <= hour) & (hour  <= floor(logout_time/3600))) |
    ((login_day != logout_day) & ((floor(login_time/3600) <= hour) | (hour  <= floor(logout_time/3600))) ), 
    list(count=.N, hour=hour, event="usage"),
    by=user_id
  ], 0:23)), user_id, hour
)
comp.user.short[,norm := count/max(count), by=user_id]
compuserbyID <- acast(comp.user.short, user_id ~ hour, value.var = "norm", fill = 0)

@@

kmUserPlotter(5, compuserbyID, comp.user.short)

>>>>

comp.user.short <- setkey(rbindlist(
  Map(function(hour) censor.dt[
    ((login_day == logout_day) & (floor(login_time/3600) <= hour) & (hour  <= floor(logout_time/3600))) |
    ((login_day != logout_day) & ((floor(login_time/3600) <= hour) | (hour  <= floor(logout_time/3600))) ), 
    list(count=.N, hour=hour, event="usage"),
    by=user_id
  ], 0:23)), user_id, hour
)

comp.user.short[,norm := count/max(count), by=user_id]
compuserbyID <- acast(comp.user.short, user_id ~ hour, value.var = "norm", fill = 0)

@@

## let's figure out user clusters
## then join censor.dt to user clusters
## then track those clusters as:
##  panel col, color for each cluster (all in same row, since y axis shared)
##  yaxis - cluster size / total user base at that time?
##  line for current total in cluster
##  width to represent turnover?  like ymax = count + additions, ymin = count - losses
##  x axis - week; day will be too noisy w/ turnover / count?

user.clusters <- kmParse(comp.user.short, 5, key="user_id", refevent="usage")
censor.dt[user.clusters$clustering][,
  list(leave=max(logout_time), join=min(login_time)), by=list(user_id,cluster)
]
